### 2020-06-11 README.Rmd
starting to work on plotting hit error
Done run_cv()

```{r, eval = run_bw}
# Big Woods
tic()
bw_cv_predict <- focal_vs_comp_bw %>%
  run_cv(model_specs = bw_specs, max_dist = max_dist, cv_grid = bw_cv_grid)
toc()
```

@@

We have a problem: not all focal trees have a CV predicted value of growth_hat

```{r, eval = run_bw}
# Big Woods
bw_growth_df %>% 
  left_join(bw_cv_predict, by = 'focal_ID', suffix = c('', '_cv')) %>% 
  mutate(has_cv = !is.na(growth_hat_cv)) %>% 
  st_as_sf() %>% 
  ggplot() +
  geom_sf(size = 0.1, aes(col = has_cv))
```

```{r, eval = run_bw}
bw_growth_df %>% 
  left_join(bw_cv_predict, by = 'focal_ID', suffix = c('', '_cv')) %>%
  filter(!is.na(growth_hat_cv)) %>% 
  as_tibble() %>% 
  summarise(
    rmse_cv = sqrt(mean((growth - growth_hat_cv)^2)),
    rmse = sqrt(mean((growth - growth_hat)^2)), 
    n = n() 
  )
```

@@

>>>>

```{r, eval = run_bw}
# Big Woods
if (!file.exists("bw_cv_predict.Rdata")) {
tic()
bw_cv_predict <- focal_vs_comp_bw %>%
  run_cv(model_specs = bw_specs, max_dist = max_dist, cv_grid = bw_cv_grid)
toc()
  save(bw_cv_predict, file = "bw_cv_predict.Rdata")
} else {
  load("bw_cv_predict.Rdata")
}
```

@@

```{r, eval = run_bw}
# Big Woods
bw_growth_df <- bw_growth_df %>% 
  left_join(bw_cv_predict, by = "focal_ID", suffix = c('', '_cv')) %>% 
  mutate(has_cv = !is.na(growth_hat))

ggplot(bw_growth_df) +
  geom_sf(size = 0.1, aes(col = has_cv))
```

It appears not all trees have a CV predicted value of `growth_hat`. This is because either:

* The tree is part of the buffer
* The tree was dropped in the `create_focal_vs_comp()` phase

```{r, eval = run_bw}
# This code is a hideous sanity check of the two facts above. To delete.
trees_dropped_during_create_focal_vs_comp <- 
  setdiff(unique(bw_growth_df$focal_ID), unique(focal_vs_comp_bw$focal_ID)) %>% 
  sort()
trees_with_no_cv <- bw_growth_df %>% 
  filter(!has_cv) %>% 
  pull(focal_ID) %>% 
  sort()
mean(trees_dropped_during_create_focal_vs_comp == trees_with_no_cv)
```

Let's remove these trees that have no

```{r, eval = run_bw}
bw_growth_df <- bw_growth_df %>% 
  filter(!is.na(growth_hat))
```

Let's compute summary statistics of our cross-validated errors:

```{r, eval = run_bw}
# Big Woods
bw_growth_df %>% 
  as_tibble() %>% 
  summarise(
    rmse_cv = sqrt(mean((growth - growth_hat)^2)),
    rmse = sqrt(mean((growth - growth_hat)^2)), 
    n = n() 
  )
```

Let's visualize the spatial distribution of our cross-validated errors:

```{r, eval = run_bw}
# Big Woods
bw_growth_df <- bw_growth_df %>%
  mutate(
    error = growth - growth_hat,
    error_bin = cut_number(error, n = 5),
    error_compress = ifelse(error < -0.75, -0.75, ifelse(error > 0.75, 0.75, error))
  )

ggplot(bw_growth_df) +
  geom_sf(aes(col = error_compress), size = 0.4) +
  scale_color_gradient2(
    low = "#ef8a62", mid = "#f7f7f7", high = "#67a9cf", 
    name = expression(paste("Residual (cm ", y^{-1}, ")")),
    breaks = seq(from = -0.75, to = 0.75, by = 0.25),
    labels = c("< -0.75", "-0.5", "0.25", "0", "0.25", "0.5", "> 0.75")
  ) +
  labs(x = "Meter", y = "Meter")
```

@@

```{r, eval = run_bw}

# plot_beta0(bw_fit_model)
